Improving Software Maintainability through Automated Refactoring of Code Clones

### 2019-08-16 icse/paper.tex
Fixed some

\subsection{Calculating a maintainability score}\label{sec:metricformula}
In this study, we use four metrics to determine maintainability \ref{sec:metrics}. For our experiments, we want to aggregate the scores obtained by these metrics to draw a conclusion about the maintainability increase or decrease after applying a refactoring. We base our aggregation on the following assumptions:
\begin{itemize}
  \item All metrics are equal in terms of weight towards system maintenance effort.
  \item Higher values for the metrics imply lower maintainability.
  \item The obtained increase of the metric divided by the average distance from zero over our corpus weights the metric equally against the other metrics.
\end{itemize}
We calculate the average deviation as follows:
\begin{equation}\label{eq:scoredev}
A = \frac{\sum_{x \in M} abs(x)}{|M|}
\end{equation}
Where \textit{M} is the multiset of all change in a certain metric for all refactorings over all systems in  obtained for a certain metric over our corpus and \textit{|M|} is the cardinality of this set. We then calculate the maintainability for a specific refactoring as follows:
\begin{equation}\label{eq:scoreref}
A_M = \frac{dup}{A_{dup}} + \frac{com}{A_{com}} + \frac{par}{A_{par}} + \frac{vol}{A_{vol}}
\end{equation}
Where \textit{dup} is the decrease in duplication, \textit{com} is the decrease in complexity, \textit{par} is the decrease is method parameters and \textit{vol} is the decrease in system volume after the refactoring is applied. When comparing the maintainability of a set of refactorings we divide the sum of the maintainability score by the amount of clone instances of all refactored clones in the set.

>>>>

\subsection{Calculating a maintainability score}\label{sec:metricformula}
In this study, we use four metrics to determine maintainability (see Sec.~\ref{sec:metrics}). For our experiments, we aggregate the scores obtained by these metrics to draw a conclusion about the maintainability increase or decrease after applying a refactoring. We base our aggregation on the following assumptions:
\begin{itemize}
  \item All metrics are equal in terms of weight towards system maintenance effort.
  \item Higher values for the metrics imply lower maintainability.
  \item The obtained increase of the metric divided by the average distance from zero over our corpus weights the metric equally against the other metrics.
\end{itemize}
We calculate the average deviation as follows:
\begin{equation}\label{eq:scoredev}
A = \frac{\sum_{x \in M} abs(x)}{|M|}
\end{equation}
Where \textit{M} is the multiset of all change in a certain metric for all refactorings over all systems in  obtained for a certain metric over our corpus and \textit{|M|} is the cardinality of this set. We then calculate the maintainability for a specific refactoring as follows:
\begin{equation}\label{eq:scoreref}
A_M = \frac{dup}{A_{dup}} + \frac{com}{A_{com}} + \frac{par}{A_{par}} + \frac{vol}{A_{vol}}
\end{equation}
Where \textit{dup} is the decrease in duplication, \textit{com} is the decrease in complexity, \textit{par} is the decrease is method parameters and \textit{vol} is the decrease in system volume after the refactoring is applied. When comparing the maintainability of a set of refactorings we divide the sum of the maintainability score by the amount of clone instances of all refactored clones in the set.
